---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Simple linear regression 
Simple linear regression is a statistical method that allows us to summarize and study relationships between two vairables. This package provides simple linear regression model using the least squares estimates. 

# Usage 
sim_lin_R(x, y)

# Arguments 
* `x`: a numeric vector.
* `y`: a numeric vector.

# Values
`sim_lin_R` returns a list containing the following components:

*  `coefficient`: the estimated regression coefficents, intercept and slope.
*  `standard_error`: the estimated standard errors for the coefficients,intercept and slope. 
*  `conf_interval`: the 95% confidence intervals for population intercept and slope.  
*  `residuals`: the residuals, that is response minus fitted values.
*  `predicted`: the predicted value for each observation

# Example
We will use the `cars` dataset to show how to use `simplinear` since it is a standard built-in dataset. This dataset can be accessed this dataset simply by typing in cars in your R console. It consists of 50 observations(rows) and 2 variables (columns) – `dist` and `speed`. 

```{r }
library("simlinear")
```

Let `speed` be the predictor variable (x) and `dist`, stopping distance, be the response variable (y). Now, we fit the simple linear model. Note, x and y are two numeric vector with the same length. 
```{r}
slm <- simp_lin_R(x = cars$speed, y = cars$dist)
```
The scatterplot of the observed data and the estimated line of best fit.
```{r}
plot(cars$dist~cars$speed, xlab = 'speed', ylab = 'dist', pch = 20)
abline(a = slm$coef[1,1], b = slm$coef[2,1], lty = 1)
```
The standard errors for the intercept and slope.
```{r}
slm$standard_error
```
The 95% confidence intervals for the intercept and slope.
```{r}
slm$conf_interval
```
The residuals shown in scatter plot. 
```{r}
plot(slm$residuals,pch=20)
```

